---
title: "02-data-science-is-a-verb.Rmd"
author: "Augustina Ragwitz"
date: !r Sys.Date()
output: html_document
params:
  meetup_api_key: !r Sys.getenv("API_KEY_MEETUP_RLADIES")
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(purrr)
library(tidyr)
```

# Wrangle + Rectangle

In R, a lot of tools let you do this in one step because the authors know that's where you're heading.

## From API

## From Webpage (HTML)

```{r}
download.file("https://www.meetup.com/topics/", "downloads/meetup_topics.html")
```

```{r}
library(rvest)

topics_html <- read_html("downloads/meetup_topics.html")

# Find the node by manually browsing the web page and using Developer Tools to view the page source.
topics <- topics_html %>% 
  html_nodes("#meetupBody > div.view > section:nth-child(34) > div > ul")

links <- topics %>% 
  html_nodes("li > a") %>%
  html_attr("href")

names <- topics %>% 
  html_nodes("li > a") %>%
  html_text()

topics_df <- data_frame(links=links, names=names)

```

## From PDF

What industry codes should be included in "Tech Industry"?

Paytas, Jerry, and Dan Berglund. "Technology industries and occupations for NAICS industry data." Pittsburgh: Carnegie Mellon Center for Economic Development and State Science and Technology Institute (2004). http://ssti.org/report-archive/NAICS_Tech1.pdf

Markusen, Ann, et al. "Gauging Metropolitan “High-Tech” and “I-Tech” Activity." Minneapolis, MN (2001). https://s3.amazonaws.com/academia.edu.documents/34059711/hightech.pdf


```{r naics_tech_codes_download, echo=FALSE}
download.file("http://ssti.org/report-archive/NAICS_Tech1.pdf", "downloads/ssti_naics_tech_codes.pdf")
```

```{r extract_pdf_table}
library(tabulizer)

naics_extracts <- extract_tables("downloads/ssti_naics_tech_codes.pdf",
                                  pages=c(4), method="data.frame") %>%
  reduce(bind_rows)

```


# Chronicle

You should tell a story!

Use complete sentences!

Examples...